The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-05-01 article.tex
Moved the reference earlier.
Rerun the numbers on latest 2.0 code base.

The SMILES parsing has been replaced by code from the external Beam project~\cite{Beam,Weininger1988}.
This BSD-licensed SMILES parser is a complete implementation of the SMILES
and OpenSMILES (\url{http://opensmiles.org/}) specifications by one of the
authors (including stereochemistry), and is independent of
the CDK library. The SmilesParser API uses this library underneath, and the
Beam API is hidden by this class. Basic usage is as follows:

@@

\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.51s & 108.2K & 9 & 0.97s & 2.5M & 23.21\\
 &  & sdf & 0 & 7.21s & 355.4K & 25 & 3.75s & 683.3K & 1.92\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m39.3s & 193.9K & 9 & 12.17s & 8.3M & 42.67\\
 &  & sdf & 0 & 3m17.29s & 510.4K & 0 & 1m7.23s & 1.5M & 2.93\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -mark}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.91s & 106.3K & 9 & 1.03s & 2.4M & 22.24\\
 &  & sdf & 0 & 8.71s & 294.2K & 25 & 3.93s & 652K & 2.22\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m45.78s & 191.5K & 9 & 17.98s & 5.6M & 29.24\\
 &  & sdf & 0 & 4m12.01s & 399.6K & 0 & 1m14.95s & 1.3M & 3.36\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -sssr}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 27.4s & 88.9K & 9 & 1.48s & 1.6M & 18.51\\
 &  & sdf & 0 & 11.84s & 216.4K & 25 & 4.08s & 628K & 2.9\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 12m4.62s & 139K & 9 & 28.07s & 3.6M & 25.81\\
 &  & sdf & 0 & 7m9.58s & 234.4K & 0 & 1m24.16s & 1.2M & 5.1\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -all}} & \multirow{2}{*}{ChEBI 149} & smi & 2126 & 45.28s & 53.8K & 26 & 1.27s & 1.9M & 35.65\\
 &  & sdf & 16 & 36.56s & 70.1K & 40 & 4.13s & 620.4K & 8.85\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 88 & 12m40.2s & 132.5K & 9 & 26.48s & 3.8M & 28.71\\
 &  & sdf & 90 & 8m5.64s & 207.4K & 0 & 1m18.99s & 1.3M & 6.15\\

@@

\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 36.58s & 66.6K & 9 & 1.83s & 1.3M & 19.99\\
 &  & sdf & 35 & 21.15s & 121.1K & 26 & 4.77s & 537.2K & 4.43\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m33.86s & 115.2K & 9 & 42.41s & 2.4M & 20.61\\
 &  & sdf & 0 & 8m59.82s & 186.6K & 0 & 1m44.86s & 960.4K & 5.15\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.6s & 1.5M & 22.27 \\
 &  & sdf & 35 & 20.91s & 122.5K & 25 & 4.47s & 573.2K & 4.68 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m26.02s & 116.3K & 34 & 28.14s & 3.6M & 30.78 \\
 &  & sdf & 0 & 8m59.38s & 186.7K & 1 & 1m19.86s & 1.3M & 6.75 \\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 32.42s & 75.1K & 9 & 10.33s & 235.8K & 3.14\\
 &  & sdf & 13 & 17s & 150.7K & 29 & 14.49s & 176.8K & 1.17\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 14m25.82s & 116.3K & 9 & 5m30.66s & 304.6K & 2.62\\
 &  & sdf & 1 & 8m51.33s & 189.5K & 0 & 6m50.92s & 245.1K & 1.29\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -gen2d \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 24m28.02s & 1.7K & 9 & 35.7s & 68.2K & 41.12\\
 &  & sdf & 13 & 35m12.03s & 1.2K & 29 & 42.08s & 60.9K & 50.19\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 3h27m7s & 8.1K & 9 & 18m2.59s & 93K & 11.48\\
 &  & sdf & 1 & 5h58m30s & 4.7K & 0 & 19m54.12s & 84.3K & 18.01\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m38s & 24.9K & 9 & 10.4s & 234.2K & 9.42 \\
 &  & sdf & 0 & 2m11.03s & 19.6K & 25 & 14.22s & 180.2K & 9.21 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 42m56.15s & 39.1K & 9 & 6m38.67s & 252.6K & 6.46 \\
 &  & sdf & 0 & 47m5.58s & 35.6K & 0 & 7m46.85s & 215.7K & 6.05 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type maccs}} & \multirow{2}{*}{ChEBI 149} & smi & 2150 & 1h37m35s & 416 & 9 & 19.8s & 123K & 295.71\\
 &  & sdf & 48 & 1h44m17s & 409 & 25 & 22.33s & 114.7K & 280.21\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 214 & 20h24m57s & 1.4K & 9 & 13m27.11s & 124.8K & 91.06\\
 &  & sdf & 225 & 24h41m46s & 1.1K & 0 & 13m41.83s & 122.5K & 108.18\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type circ}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & NA & - & 9 & 4.47s & 544.9K & 0\\
 &  & sdf & 0 & NA & - & 25 & 7.04s & 364K & 0\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & NA & - & 9 & 2m45.68s & 607.8K & 0\\
 &  & sdf & 0 & NA & - & 0 & 3m59.23s & 420.9K & 0\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -mark}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0.4s & 6.1M & 0 & 0.06s & 40.6M & 6.7\\
 &  & sdf & 0 & 1.5s & 1.7M & 0 & 0.18s & 14.2M & 8.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 6.48s & 15.5M & 0 & 5.81s & 17.3M & 1.1\\
 &  & sdf & 0 & 54.72s & 1.8M & 0 & 7.72s & 13M & 7.1\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -sssr}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 4.89s & 498.1K & 0 & 0.51s & 4.8M & 9.6\\
 &  & sdf & 0 & 4.63s & 553.4K & 0 & 0.33s & 7.8M & 14\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3m25.32s & 490.5K & 0 & 15.9s & 6.3M & 12.9\\
 &  & sdf & 0 & 3m52.29s & 433.5K & 0 & 16.93s & 5.9M & 13.7\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -all}}  & \multirow{2}{*}{ChEBI 149}  & smi & 14 & 22.77s & 107K & 17 & 0.3s & 8.1M & 75.9\\
 &  & sdf & 16 & 29.35s & 87.3K & 15 & 0.38s & 6.7M & 77.2\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 88 & 4m0.9s & 418K & 0 & 14.31s & 7M & 16.8\\
 &  & sdf & 90 & 4m48.35s & 349.2K & 0 & 11.76s & 8.6M & 24.5\\

@@

\multirow{4}{*}{cansmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 14.07s & 173.1K & 0 & 0.86s & 2.8M & 16.4\\
 &  & sdf & 35 & 13.94s & 183.8K & 1 & 1.02s & 2.5M & 13.7\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m54.56s & 284K & 0 & 30.24s & 3.3M & 11.7\\
 &  & sdf & 0 & 5m42.53s & 294K & 0 & 37.63s & 2.7M & 9.1\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149} & smi & 0 & 13.12s & 185.7K & 7 & 0.63s & 3.9M & 20.8 \\
 &  & sdf & 35 & 13.7s & 187K & 0 & 0.72s & 3.6M & 19 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 5m46.72s & 290.4K & 25 & 15.97s & 6.3M & 21.7 \\
 &  & sdf & 0 & 5m42.09s & 294.4K & 1 & 12.63s & 8M & 27.1 \\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt sdf}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 9.91s & 245.8K & 0 & 9.36s & 260.2K & 1.1\\
 &  & sdf & 13 & 9.79s & 261.7K & 4 & 10.74s & 238.6K & 0.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 5m46.52s & 290.6K & 0 & 5m18.49s & 316.2K & 1.1\\
 &  & sdf & 1 & 5m34.04s & 301.5K & 0 & 5m43.69s & 293K & 1\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -gen2d \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 24m5.51s & 1.7K & 0 & 34.73s & 70.1K & 41.6\\
 &  & sdf & 13 & 35m4.82s & 1.2K & 4 & 38.33s & 66.8K & 54.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3h18m28s & 8.5K & 0 & 17m50.42s & 94.1K & 11.1\\
 &  & sdf & 1 & 5h55m13s & 4.7K & 0 & 18m46.89s & 89.4K & 18.9\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 1m15.49s & 32.3K & 0 & 9.43s & 258.3K & 8 \\
 &  & sdf & 0 & 2m3.82s & 20.7K & 0 & 10.47s & 244.7K & 11.8 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 34m16.85s & 49K & 0 & 6m26.5s & 260.6K & 5.3 \\
 &  & sdf & 0 & 43m48.29s & 38.3K & 0 & 6m39.62s & 252K & 6.6 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type maccs}}  & \multirow{2}{*}{ChEBI 149}  & smi & 38 & 1h37m12s & 418 & 0 & 18.83s & 129.4K & 309.7\\
 &  & sdf & 48 & 1h44m10s & 410 & 0 & 18.58s & 137.9K & 336.4\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 214 & 20h16m18s & 1.4K & 0 & 13m14.94s & 126.7K & 91.8\\
 &  & sdf & 225 & 24h38m29s & 1.1K & 0 & 12m34.6s & 133.5K & 117.6\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type circ}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 &  & - & 0 & 3.5s & 695.9K & \\
 &  & sdf & 0 &  & - & 0 & 3.29s & 778.8K & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 &  & - & 0 & 2m33.51s & 656K & \\
 &  & sdf & 0 &  & - & 0 & 2m52s & 585.5K & \\

>>>>

The SMILES~\cite{Weininger1988} parsing has been replaced by code from the external Beam project~\cite{Beam}.
This BSD-licensed SMILES parser is a complete implementation of the SMILES
and OpenSMILES (\url{http://opensmiles.org/}) specifications by one of the
authors (including stereochemistry), and is independent of
the CDK library. The SmilesParser API uses this library underneath, and the
Beam API is hidden by this class. Basic usage is as follows:

@@

\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.51s & 108.2K & 9 & 0.85s & 2.9M & 26.48\\
 &  & sdf & 0 & 7.21s & 355.4K & 25 & 3s & 854.1K & 2.4\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m39.3s & 193.9K & 9 & 10.74s & 9.4M & 48.35\\
 &  & sdf & 0 & 3m17.29s & 510.4K & 0 & 53.27s & 1.9M & 3.7\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-mark}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.91s & 106.3K & 9 & 1.06s & 2.3M & 21.61\\
 &  & sdf & 0 & 8.71s & 294.2K & 25 & 3.11s & 823.9K & 2.8\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m45.78s & 191.5K & 9 & 17.09s & 5.9M & 30.77\\
 &  & sdf & 0 & 4m12.01s & 399.6K & 0 & 1m6.54s & 1.5M & 3.79\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-sssr}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 27.4s & 88.9K & 9 & 1.43s & 1.7M & 19.16\\
 &  & sdf & 0 & 11.84s & 216.4K & 25 & 3.78s & 677.8K & 3.13\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 12m4.62s & 139K & 9 & 27.16s & 3.7M & 26.68\\
 &  & sdf & 0 & 7m9.58s & 234.4K & 0 & 1m8.17s & 1.5M & 6.3\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-all}} & \multirow{2}{*}{ChEBI 149} & smi & 2126 & 45.28s & 53.8K & 26 & 1.26s & 1.9M & 35.94\\
 &  & sdf & 16 & 36.56s & 70.1K & 40 & 3.51s & 730K & 10.42\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 88 & 12m40.2s & 132.5K & 9 & 24.97s & 4M & 30.44\\
 &  & sdf & 90 & 8m5.64s & 207.4K & 0 & 1m5.68s & 1.5M & 7.39\\

@@

\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 36.58s & 66.6K & 9 & 1.91s & 1.3M & 19.15\\
 &  & sdf & 35 & 21.15s & 121.1K & 26 & 4.37s & 586.3K & 4.84\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m33.86s & 115.2K & 9 & 40.84s & 2.5M & 21.4\\
 &  & sdf & 0 & 8m59.82s & 186.6K & 0 & 1m29.33s & 1.1M & 6.04\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.47s & 1.7M & 24.24\\
 &  & sdf & 35 & 20.91s & 122.5K & 25 & 4.55s & 563.1K & 4.6\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m26.02s & 116.3K & 37 & 26.2s & 3.8M & 33.05\\
 &  & sdf & 0 & 8m59.38s & 186.7K & 1 & 1m12.49s & 1.4M & 7.44\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 32.42s & 75.1K & 9 & 10.39s & 234.4K & 3.12\\
 &  & sdf & 13 & 17s & 150.7K & 25 & 13.96s & 183.5K & 1.22\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 14m25.82s & 116.3K & 9 & 5m26.29s & 308.6K & 2.65\\
 &  & sdf & 1 & 8m51.33s & 189.5K & 0 & 6m34.5s & 255.3K & 1.35\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-gen2d \\-ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 24m28.02s & 1.7K & 9 & 35.86s & 67.9K & 40.94\\
 &  & sdf & 13 & 35m12.03s & 1.2K & 25 & 42.43s & 60.4K & 49.78\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 3h27m7s & 8.1K & 9 & 17m44.64s & 94.6K & 11.67\\
 &  & sdf & 1 & 5h58m30s & 4.7K & 0 & 19m42.77s & 85.1K & 18.19\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m38s & 24.9K & 9 & 10.28s & 236.9K & 9.53\\
 &  & sdf & 0 & 2m11.03s & 19.6K & 25 & 13.03s & 196.6K & 10.06\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 42m56.15s & 39.1K & 9 & 6m34.67s & 255.2K & 6.53\\
 &  & sdf & 0 & 47m5.58s & 35.6K & 0 & 7m52.32s & 213.2K & 5.98\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type maccs}} & \multirow{2}{*}{ChEBI 149} & smi & 2150 & 1h37m35s & 416 & 9 & 19.51s & 124.8K & 300.1\\
 &  & sdf & 48 & 1h44m17s & 409 & 25 & 21.25s & 120.6K & 294.45\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 214 & 20h24m57s & 1.4K & 9 & 13m31.21s & 124.1K & 90.6\\
 &  & sdf & 225 & 24h41m46s & 1.1K & 0 & 13m26.41s & 124.9K & 110.25\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type circ}} & \multirow{2}{*}{ChEBI 149} & smi & 0 &  & - & 9 & 4.37s & 557.4K & 0\\
 &  & sdf & 0 &  & - & 25 & 6.81s & 376.2K & 0\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 &  & - & 9 & 2m43.45s & 616.1K & 0\\
 &  & sdf & 0 &  & - & 0 & 3m42.01s & 453.6K & 0\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-mark}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 0.4s & 6.1M & 0 & 0.21s & 11.6M & 1.9\\
 &  & sdf & 0 & 1.5s & 1.7M & 0 & 0.11s & 23.3M & 13.6\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 6.48s & 15.5M & 0 & 6.35s & 15.9M & 1\\
 &  & sdf & 0 & 54.72s & 1.8M & 0 & 13.27s & 7.6M & 4.1\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-sssr}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 4.89s & 498.1K & 0 & 0.58s & 4.2M & 8.4\\
 &  & sdf & 0 & 4.63s & 553.4K & 0 & 0.78s & 3.3M & 5.9\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 3m25.32s & 490.5K & 0 & 16.42s & 6.1M & 12.5\\
 &  & sdf & 0 & 3m52.29s & 433.5K & 0 & 14.9s & 6.8M & 15.6\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\-all}} & \multirow{2}{*}{ChEBI 149} & smi & 14 & 22.77s & 107K & 17 & 0.41s & 5.9M & 55.5\\
 &  & sdf & 16 & 29.35s & 87.3K & 15 & 0.51s & 5M & 57.5\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 88 & 4m0.9s & 418K & 0 & 14.23s & 7.1M & 16.9\\
 &  & sdf & 90 & 4m48.35s & 349.2K & 0 & 12.41s & 8.1M & 23.2\\

@@

\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 14.07s & 173.1K & 0 & 1.06s & 2.3M & 13.3\\
 &  & sdf & 35 & 13.94s & 183.8K & 1 & 1.37s & 1.9M & 10.2\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 5m54.56s & 284K & 0 & 30.1s & 3.3M & 11.8\\
 &  & sdf & 0 & 5m42.53s & 294K & 0 & 36.06s & 2.8M & 9.5\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 13.12s & 185.7K & 7 & 0.62s & 3.9M & 21.2\\
 &  & sdf & 35 & 13.7s & 187K & 0 & 1.55s & 1.7M & 8.8\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 5m46.72s & 290.4K & 28 & 15.46s & 6.5M & 22.4\\
 &  & sdf & 0 & 5m42.09s & 294.4K & 1 & 19.22s & 5.2M & 17.8\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 9.91s & 245.8K & 0 & 9.54s & 255.3K & 1\\
 &  & sdf & 13 & 9.79s & 261.7K & 0 & 10.96s & 233.8K & 0.9\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 5m46.52s & 290.6K & 0 & 5m15.55s & 319.1K & 1.1\\
 &  & sdf & 1 & 5m34.04s & 301.5K & 0 & 5m41.23s & 295.1K & 1\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\-gen2d \\-ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 24m5.51s & 1.7K & 0 & 35.01s & 69.6K & 41.3\\
 &  & sdf & 13 & 35m4.82s & 1.2K & 0 & 39.43s & 65K & 53.4\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 3h18m28s & 8.5K & 0 & 17m33.9s & 95.6K & 11.3\\
 &  & sdf & 1 & 5h55m13s & 4.7K & 0 & 18m49.5s & 89.2K & 18.9\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type path}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & 1m15.49s & 32.3K & 0 & 9.43s & 258.3K & 8\\
 &  & sdf & 0 & 2m3.82s & 20.7K & 0 & 10.03s & 255.5K & 12.3\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 34m16.85s & 49K & 0 & 6m23.93s & 262.3K & 5.4\\
 &  & sdf & 0 & 43m48.29s & 38.3K & 0 & 6m59.05s & 240.3K & 6.3\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type maccs}} & \multirow{2}{*}{ChEBI 149} & smi & 38 & 1h37m12s & 418 & 0 & 18.66s & 130.5K & 312.6\\
 &  & sdf & 48 & 1h44m10s & 410 & 0 & 18.25s & 140.4K & 342.5\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 214 & 20h16m18s & 1.4K & 0 & 13m20.47s & 125.8K & 91.2\\
 &  & sdf & 225 & 24h38m29s & 1.1K & 0 & 12m33.14s & 133.7K & 117.8\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\-type circ}} & \multirow{2}{*}{ChEBI 149} & smi & 0 &  & - & 0 & 3.52s & 692K & \\
 &  & sdf & 0 &  & - & 0 & 3.81s & 672.5K & \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 &  & - & 0 & 2m32.71s & 659.4K & \\
 &  & sdf & 0 &  & - & 0 & 2m48.74s & 596.8K & \\
